### 2010-02-24 sarahDraft.tex
Added Chrisna's fixed equations

	The mean ...
 	\begin{align*}
        E[A] 
            &= \sum_{i=1}^{n-1} P(X_i = 0, X_{i+1} = 1) \\
            &= \sum_{i=1}^{n-1} (1-p)p \\
            &= (n-1)(1-p)p
    \end{align*}
    \begin{align*}
        E[B]
            &= \sum_{i=1}^{n-1} P(X_i = 1, X_{i+1} = 1) \\
            &= \sum_{i=1}^{n-1} p*p \\
            &= (n-1)p^2
    \end{align*}
	\begin{align*}
        E[\hat{s}] 
            &= E[A] - E[B] \\
            &= (n-1)\bigg((1-p)p - p^2\bigg)
    \end{align*}

	The standard deviation...
	\begin{align*}
        Var[A] 
            &= \sum_{i=1}^{n-1} Var[A] + 2\sum_{i=1}^{n-2} Cov[I_i = (0, 1),
               I_{i+1} = (1, 1)] \\
            &= (n-1)P((0, 1))(1-P((0, 1))) + 2\sum_{i=1}^{n-2}\bigg(E[I_i=(0, 
               1), I_{i+1} = (0, 1)] - E[I_i = (0, 1)]E[I_{i+1} = (0, 1)]\bigg)
               \\
            &= (n-1)(1-p)p(1-(1-p)p) + 2\sum_{i=1}^{n-2}\bigg(0 - (1-p)p(1-p)p
               \bigg) \\
            &= (1-p)p(-1+n+5p-3np-5p^2+3np^2)
    \end{align*}
    \begin{align*}
        Var[B] 
            &= \sum_{i=1}^{n-1} Var[B] + 2\sum_{i=1}^{n-2} Cov[I_i = (1, 1),
               I_{i+1} = (1, 1)] \\
            &= (n-1)P((1, 1))(1-P((1, 1))) + 2\sum_{i=1}^{n-2}\bigg(E[I_i=(1,   
               1), I_{i+1} = (1, 1)] - E[I_i = (1, 1)]E[I_{i+1} = (1, 1)]\bigg) 
               \\
            &= (n-1)p^2(1-p^2) + 2(n-2)(p^3-p^4) \\
            &= (1-p)p^2(-1+n-5p+3np)
    \end{align*}
	\begin{align*}
		2Cov[A, B]  
			&= 2 \sum_{i=1}^{n-1} \sum_{j=1}^{n-1} Cov[A, B]\\
			&= 2 \bigg(\sum_{i=1}^{n-2} Cov[AB] + \sum_{i=1}^{n-2} Cov[BA] +
				\\ \sum_{i=1}^{n-1} Cov[X_i = 0 \text{ or } 1, X_{i+1} = 1]\bigg) \\
			&= 2 \bigg(\sum_{i=1}^{n-2} E[AB] - E[A]E[B] + 
				\sum_{i=1}^{n-2} E[BA] - E[B]E[A] + \\
				\sum_{i=1}^{n-1} E[X_i = 0 \text{ or } 1, X_{i+1} = 1] - E[B]E[A] \\
			&= 2(n-2)(p-1)^2p^2 - 2(n-2)p^3(1-p) - 2(n-1)p^3(1-p)			
	\end{align*}	
    \begin{align*}
        Var[\hat{s}] 
            &= Var[A-B] \\
            &= Var[A] + Var[B] - 2Cov[A, B] \\
            &= (1-p)p(-1+n+8p-4np-20p^2+12np^2)
    \end{align*}

>>>>

	The mean ...
 	  % E[A]
    \begin{equation*}
        \begin{split}
        E[A]& =\sum_{i=1}^{n-1}P(X_i=0,X_{i+1}=1) \\
            & =\sum_{i=1}^{n-1}(1-p)p \\
            & =(n-1)(1-p)p \\
        \end{split}
    \end{equation*}

    % E[B]
    \begin{equation*}
        \begin{split}
        E[B]& =\sum_{i=1}^{n-1}P(X_i=1,X_{i+1}=1) \\
            & =\sum_{i=1}^{n-1}p*p \\
            & =(n-1)p^2
        \end{split}
    \end{equation*}

  % E[s-hat]
    \begin{equation*}
        \begin{split}
        E[\hat{s}]& =E[A]-E[B] \\
                  & =(n-1)\left((1-p)p-p^2\right)
        \end{split}
    \end{equation*}

	The standard deviation...
    % Var[A]
    \begin{equation*}
        \begin{split}
        Var[A]& =\sum_{i=1}^{n-1}Var[A]+2\sum_{i=1}^{n-2}Cov[I_i=(0,1),I_{i+1}=
                 (1,1)] \\
              & =(n-1)P((0,1))(1-P((0,1))) \\
              & \quad +2\sum_{i=1}^{n-2}\bigg(E[I_i=(0,1),I_{i+1}=(0,1)]-E[I_i=
                (0,1)]E[I_{i+1}=(0,1)]\bigg) \\
              & =(n-1)(1-p)p(1-(1-p)p)+2\sum_{i=1}^{n-2}\bigg(0-(1-p)p(1-p)p
                \bigg) \\
              & =(1-p)p(-1+n+5p-3np-5p^2+3np^2)
        \end{split}
    \end{equation*}

    % Var[B]
    \begin{equation*}
        \begin{split}
        Var[B]& =\sum_{i=1}^{n-1}Var[B]+2\sum_{i=1}^{n-2}Cov[I_i=(1,1),I_{i+1}=
                (1,1)] \\
              & =(n-1)P((1, 1))(1-P((1, 1))) \\
              & \quad +2\sum_{i=1}^{n-2}\bigg(E[I_i=(1,1),I_{i+1}=(1,1)]-E[I_i=
                (1,1)]E[I_{i+1}=(1,1)]\bigg) \\
              & =(n-1)p^2(1-p^2)+2(n-2)(p^3-p^4) \\
              & =(1-p)p^2(-1+n-5p+3np)
        \end{split}
    \end{equation*}

    % Cov[A, B]
    \begin{equation*}
        \begin{split}
        Cov[A,B]& =\sum_{i=1}^{n-1}\sum_{j=1}^{n-1}Cov[A,B] \\
                & =\sum_{i=1}^{n-2}Cov[A,B]+\sum_{i=1}^{n-2}Cov[B,A] \\
                & \quad +\sum_{i=1}^{n-1}Cov[X_i=0\text{ or }1,X_{i+1}=1] \\
                & =\sum_{i=1}^{n-2}E[AB]-E[A]E[B]+\sum_{i=1}^{n-2}E[BA]-
                  E[B]E[A] \\
                & \quad +\sum_{i=1}^{n-1}E[X_i=0\text{ or }1,X_{i+1}=1]-
                  E[B]E[A] \\
                & =(n-2)(p-1)^2p^2-(n-2)p^3(1-p)-(n-1)p^3(1-p)
        \end{split}
    \end{equation*}

    % Var[s-hat]
    \begin{equation*}
        \begin{split}
        Var[\hat{s}]& =Var[A-B] \\
                    & =Var[A]+Var[B]-2Cov[A,B] \\
                    & =(1-p)p(-1+n+8p-4np-20p^2+12np^2)
        \end{split}
    \end{equation*}
